Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-07 overall.tex
ongoing fixes.

Currently, ATLAS deploys 20 instances of the PanDA Broker on 4 Titan's DTNs,
5 instances per DTN\@. Each broker submits and manages the execution of 15 to
300 ATLAS jobs, one job for each Titan's worker node, and a theoretical
maximum concurrent use of 96,000 cores. Since November 2015, PanDA Brokers
have operated only in backfill mode, without a defined time allocation, and
running at the lowest priority on Titan. Therefore, ATLAS contributed to
increase the Titan's overall utilization without affecting other users.

@@

PanDA Brokers' efficiency (Fig.~\ref{fig:backfill-utilization}, red labels)
is defined as the fraction of core-hours utilized by the PanDA Brokers to
Titan’s total backfill availability during the experiment time window. The
brokers reached 18\% average efficiency, with a minimum 7.8\% efficiency on
May 2016 and a maximum 30.9\% efficiency on February 2017 (excluding the
preliminary results of March). The total backfill availability was 20.3M in
April 2016, and 17.6M in February 2017. This shows that the measured
difference in efficiency did not depend on a comparable difference in the
total backfill availability.

>>>>

Currently 20 instances of the PanDA Broker are deployed on 4 Titan DTNs, with
5 instances per DTN\@. Each broker submits and manages the execution of 15 to
300 ATLAS jobs, one job for each Titan worker node, and a theoretical maximum
concurrent use of 96,000 cores. Since November 2015, PanDA Brokers have
operated only in backfill mode, without a defined time allocation, and running
at the lowest priority on Titan.  Therefore, ATLAS contributed to an increase
of Titan's overall utilization.

% without affecting other users.

@@

PanDA Brokers' efficiency (Fig.~\ref{fig:backfill-utilization}, red labels) is
defined as the fraction (or percentage) of core-hours utilized by the PanDA
Brokers to Titan’s total backfill availability during the experiment time
window. The brokers reached 18\% average efficiency, with a minimum 7.8\%
efficiency on May 2016 and a maximum 30.9\% efficiency on February 2017
(excluding the preliminary results of March). The total backfill availability
was 20.3M in April 2016, and 17.6M in February 2017. This shows that the
measured difference in efficiency did not depend on a comparable difference in
the total backfill availability.
